% Dr. Geoff Boeing - Curriculum Vitae
% Copyright 2019 Geoff Boeing
% Email: boeing@usc.edu
% Web: https://geoffboeing.com/

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) so accented characters are a single glyph
\usepackage[utf8]{inputenc} % allow input of utf-8 encoded characters
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % automatically regionalize hyphens, quote marks, etc
\usepackage{microtype} % improves text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto} % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts

% what is your name?
\newcommand{\myname}{Geoff Boeing}

% define a default font face and set it as the body font
\usepackage{crimson} % document's serif font
\usepackage{helvet}  % document's sans serif font

% define how far to tab for list items with left-aligned date - different font faces need different widths
\newcommand{\listtabwidth}{1.75cm}

% set name font to title the document
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*}{20}
\titleformat{\section}{\sffamily\small\bfseries\lsstyle\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{24pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{12pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}

% set page margins
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% define space between list items
\newcommand{\listitemspace}{0.15em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
            \setlength{\parskip}{0em}
            \setlength{\itemsep}{\listitemspace}
            \setlength{\parsep}{\listitemspace}}}
    {\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print the month and year only when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    pdfauthor   = {\myname},
    pdfkeywords = {city planning, housing, street networks, transportation, urban design, urban informatics},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright

    % display name as the document title
    \namefont{\myname}

    % contact info
    \vspace{1em}
    \begin{minipage}[t]{0.68\textwidth}
        Department of Urban Planning and Spatial Analysis \\
        Sol Price School of Public Policy \\
        University of Southern California
        %\\Los Angeles, California, USA
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        Email: \href{mailto:boeing@usc.edu}{boeing@usc.edu} \\
        Phone: +1 213 740 2773 \\
        Web: \href{https://geoffboeing.com/}{https://geoffboeing.com/}
    \end{minipage}
    \vspace{0.5em}



    \section*{Education}

    \begin{tablist}

        \item[Ph.D.] \tab City and Regional Planning, University of California, Berkeley, 2017

        \item[M.S.]  \tab Information Management, Arizona State University, 2006

        \item[B.S.]  \tab Computer Information Systems \textit{summa cum laude}, Arizona State University, 2004

    \end{tablist}



    \section*{Academic Appointments}

    \begin{tablist}

        \item[2019--]   \tab University of Southern California \\
                             Assistant Professor, Sol Price School of Public Policy

        \item[2018--19] \tab Northeastern University \\
                             Assistant Professor, School of Public Policy and Urban Affairs \\
                             Faculty Affiliate, Network Science Institute \\
                             Faculty Affiliate, Global Resilience Institute \\
                             Core Faculty, NU Lab for Texts, Maps, and Networks

        \item[2017--18] \tab University of California, Berkeley \\
                             Postdoctoral Research Fellow, Department of City and Regional Planning

    \end{tablist}



    \section*{Research Areas}

    \begin{itemize}

        \item Urban informatics and spatial data science: computational statistics, visualization, and spatial analysis

        \item Transportation planning: access, equity, street network design, and urban form

        \item Housing: emerging technology platforms' impacts on markets, residential mobility, and segregation

    \end{itemize}



    \section*{Publications}

    \subsection*{Articles in Peer-Reviewed Journals}

    \begin{tablist}
    	
    	\item[2019] \tab Boeing, G. \enquote{Online Rental Housing Market Representation and the Digital Reproduction of Urban Inequality.} \textit{Environment and Planning A: Economy and Space} published online before print. \href{https://doi.org/10.1177/0308518X19869678}{doi:10.1177/0308518X19869678}
    	
    	\item[2019] \tab Boeing, G. \enquote{Urban Spatial Order: Street Network Orientation, Configuration, and Entropy.} \textit{Applied Network Science} 4 (1), 67. \href{https://doi.org/10.1007/s41109-019-0189-1}{doi:10.1007/s41109-019-0189-1}
    	
    	\item[2019] \tab Boeing, G. \enquote{Spatial Information and the Legibility of Urban Form: Big Data in Urban Morphology.} \textit{International Journal of Information Management} published online before print. \href{https://doi.org/10.1016/j.ijinfomgt.2019.09.009}{doi:10.1016/j.ijinfomgt.2019.09.009} 
		
        \item[2019] \tab Boeing, G. \enquote{Street Network Models and Measures for Every US City, County, Urbanized Area, Census Tract, and Zillow-Defined Neighborhood.} \textit{Urban Science} 3 (1), 28. \href{https://doi.org/10.3390/urbansci3010028}{doi:10.3390/urbansci3010028}
        
        \item[2019] \tab Padgham, M., G. Boeing, D. Cooley, N. Tierney, M. Sumner, T. Phan, and R. Beare. \enquote{An Introduction to Software Tools, Data, and Services for Geospatial Analysis of Stroke Services.} \textit{Frontiers in Neurology} 10, 743. \href{https://doi.org/10.3389/fneur.2019.00743}{doi:10.3389/fneur.2019.00743}

        \item[2018] \tab Boeing, G. \enquote{Planarity and Street Network Representation in Urban Form Analysis.} \textit{Environment and Planning B: Urban Analytics and City Science} published online before print. \href{https://doi.org/10.1177/2399808318802941}{doi:10.1177/2399808318802941}

        \item[2018] \tab Boeing, G. \enquote{Measuring the Complexity of Urban Form and Design.} \textit{Urban Design International} 23 (4), 281--292. \href{https://doi.org/10.1057/s41289-018-0072-1}{doi:10.1057/s41289-018-0072-1}

        \item[2018] \tab Boeing, G. \enquote{A Multi-Scale Analysis of 27,000 Urban Street Networks: Every US City, Town, Urbanized Area, and Zillow Neighborhood.} \textit{Environment and Planning B: Urban Analytics and City Science} published online before print. \href{https://doi.org/10.1177/2399808318784595}{doi:10.1177/2399808318784595}

        \item[2018] \tab Boeing, G. \enquote{Estimating Local Daytime Population Density from Census and Payroll Data.} \textit{Regional Studies, Regional Science} 5 (1), 179--182. \href{https://doi.org/10.1080/21681376.2018.1455535}{doi:10.1080/21681376.2018.1455535}

        \item[2018] \tab Boeing, G. \enquote{The Effects of Inequality, Density, and Heterogeneous Residential Preferences on Urban Displacement and Metropolitan Structure: An Agent-Based Model.} \textit{Urban Science} 2 (3), 76. \href{https://doi.org/10.3390/urbansci2030076}{doi:10.3390/urbansci2030076}

        \item[2018] \tab Boeing, G. \enquote{Pynamical: Model and Visualize Discrete Nonlinear Dynamical Systems, Chaos, and Fractals.} \textit{Journal of Open Source Education} 1 (1), 15. \href{https://doi.org/10.21105/jose.00015}{doi:10.21105/jose.00015}

        \item[2017] \tab Boeing, G. \enquote{OSMnx: New Methods for Acquiring, Constructing, Analyzing, and Visualizing Complex Street Networks.} \textit{Computers, Environment and Urban Systems} 65, 126--139. \href{https://doi.org/10.1016/j.compenvurbsys.2017.05.004}{doi:10.1016/j.compenvurbsys.2017.05.004}

        \item[2017] \tab Boeing, G. and P. Waddell. \enquote{New Insights into Rental Housing Markets across the United States: Web Scraping and Analyzing Craigslist Rental Listings.} \textit{Journal of Planning Education and Research} 37 (4), 457--476. \href{https://doi.org/10.1177/0739456X16664789}{doi:10.1177/0739456X16664789}

        \item[2017] \tab Boeing, G. \enquote{OSMnx: A Python Package to Work with Graph-Theoretic OpenStreetMap Street Networks.} \textit{Journal of Open Source Software} 2 (12), 1. \href{https://doi.org/10.21105/joss.00215}{doi:10.21105/joss.00215}

        \item[2016] \tab Boeing, G. \enquote{Honolulu Rail Transit: International Lessons from Barcelona in Linking Urban Form, Design, and Transportation.} \textit{Planext} 2, 28--47. \href{https://doi.org/10.17418/planext.2016.3vol.02}{doi:10.17418/planext.2016.3vol.02}

        \item[2016] \tab Boeing, G. \enquote{Visual Analysis of Nonlinear Dynamical Systems: Chaos, Fractals, Self-Similarity, and the Limits of Prediction.} \textit{Systems} 4 (4), 37. \href{https://doi.org/10.3390/systems4040037}{doi:10.3390/systems4040037}

        \item[2014] \tab Boeing, G., D. Church, H. Hubbard, J. Mickens, and L. Rudis. \enquote{LEED-ND and Livability Revisited.} \textit{Berkeley Planning Journal} 27 (1), 31--55. \href{https://doi.org/10.31235/osf.io/jpjhq}{doi:10.31235/osf.io/jpjhq}

    \end{tablist}



    \subsection*{Journal Article Manuscripts Under Review}

    \begin{tablist}

        \item[\the\year] \tab Boeing, G., J. Wegmann, and J. Jiao. \enquote{Rental Housing Spot Markets: How Online Information Exchanges Can Supplement Transacted-Rents Data.} Revise and resubmit at \textit{Journal of Planning Education and Research}.
        
        \item[\the\year] \tab Boeing, G., M. Besbris, A. Schachter, and J. Kuk. \enquote{Housing Search in the Age of Big Data: Smarter Cities or the Same Old Blind Spots?} Revise and resubmit at \textit{Housing Policy Debate}, special issue on smart cities.
        
        \item[\the\year] \tab Boeing, G. \enquote{Urban Street Network Analysis in a Computational Notebook.} Under review at \textit{Region: Journal of the European Regional Science Association}, special issue on the potential of notebooks for scientific publication.
        
        \item[\the\year] \tab Kang, W., T. Oshan, L.~J. Wolf, G. Boeing, V. Frias-Martinez, S. Gao, A. Poorthuis, W. Xu. \enquote{Defining Urban Data Science: A Roundtable Discussion.} Under review at \textit{Environment and Planning B: Urban Analytics and City Science}.

    \end{tablist}



    \subsection*{Book Chapters}

    \begin{tablist}

        \item[2019] \tab Boeing, G. \enquote{The Morphology and Circuity of Walkable and Drivable Street Networks.} In: \textit{The Mathematics of Urban Morphology} (pp. 271--287), edited by L. D'Acci. Basel, Switzerland: Birkhäuser. \href{https://doi.org/10.1007/978-3-030-12381-9_12}{doi:10.1007/978-3-030-12381-9\_12}

        \item[2017] \tab Barajas, J.~M., G. Boeing, and J. Wartell. \enquote{Neighborhood Change, One Pint at a Time: The Impact of Local Characteristics on Craft Breweries.} In: \textit{Untapped: Exploring the Cultural Dimensions of Craft Beer} (pp. 155--176), edited by N.~G. Chapman, J.~S. Lellock, and C.~D. Lippard. Morgantown, WV: West Virginia University Press. \href{https://doi.org/10.31235/osf.io/v88hh}{doi:10.31235/osf.io/v88hh}

    \end{tablist}



    \subsection*{Conference Proceedings/Compendia}

    \begin{tablist}

        \item[2019] \tab Boeing, G. \enquote{Street Network Patterns, Orientation, and Entropy around the World.} Transportation Research Board 98\textsuperscript{th} Annual Meeting. Washington, DC. Jan 13--17. \href{https://trid.trb.org/view/1573315}{https://trid.trb.org/view/1573315}

        \item[2018] \tab Boeing, G. \enquote{The Relative Circuity of Walkable and Drivable Urban Street Networks.} Transportation Research Board 97\textsuperscript{th} Annual Meeting. Washington, DC. Jan 7--11. \href{https://trid.trb.org/view/1495502}{https://trid.trb.org/view/1495502}

    \end{tablist}



    \subsection*{Edited Articles and Reviews}

    \begin{tablist}

        \item[2018] \tab Boeing, G. \enquote{Automated Street Network Analysis for Urban Planners with OSMnx.} \textit{Planning and Technology Today} 117 (Spring), 10--11. \href{https://doi.org/10.31235/osf.io/mkbp3}{doi:10.31235/osf.io/mkbp3}

        \item[2017] \tab Boeing, G. \enquote{A Review of the Structure and Dynamics of Cities: Urban Data Analysis and Theoretical Modeling.} \textit{Journal of the American Planning Association} 83 (4), 418. \href{https://doi.org/10.1080/01944363.2017.1362306}{doi:10.1080/01944363.2017.1362306}

        \item[2017] \tab Boeing, G. \enquote{Understanding Cities through Networks and Flows.} \textit{Berkeley Planning Journal} 28 (1), 118--123. \href{https://doi.org/10.31235/osf.io/mxngm}{doi:10.31235/osf.io/mxngm}

        \item[2016] \tab Boeing, G. \enquote{How Our Neighborhoods Lost Food, and How They Can Get It Back.} \textit{Progressive Planning} 206 (Winter), 35--37. \href{https://doi.org/10.31235/osf.io/a5e2q}{doi:10.31235/osf.io/a5e2q}

    \end{tablist}



    \subsection*{Reports and Working Papers}

    \begin{tablist}

        \item[2018] \tab Waddell, P., G. Boeing, M. Gardner, and E. Porter. \enquote{An Integrated Pipeline Architecture for Modeling Urban Land Use, Travel Demand, and Traffic Assignment.} US Department of Energy SMART Mobility Urban Science Pillar: Coupling Land Use Models and Network Flow Models. Technical report. \href{https://doi.org/10.31235/osf.io/74zaw}{doi:10.31235/osf.io/74zaw}

    \end{tablist}



    \subsection*{Patents}

    \begin{tablist}

        \item[2014] \tab Beck, A.~E., G. Boeing, and D. Shannon. \textit{Systems and Methods for Analyzing Requirements}. United States patent US8650186B2, European patent EP2413256, Australian patent AU2011204935, Canadian patent CA2747481, Chinese patent CN102346763.

    \end{tablist}



    \subsection*{Manuscripts in Preparation}

    \begin{tablist}
        
        \item[\the\year] \tab Boeing, G. and W. Riggs. \enquote{Converting One-Way Streets to Two-Way Streets to Improve Transportation Network Efficiency and Reduce Vehicle Distance Traveled and Emissions.} Target: \textit{Transportation Research Record}, Summer 2019.
        
        \item[\the\year] \tab Kontokosta, C., L. Bettencourt, M. González, S. Williams, and G. Boeing. \enquote{Urban Science and Analytics.} \textit{Journal of Planning Education and Research}, Fall 2019.

        \item[\the\year] \tab Boeing, G. \enquote{Off the Grid: The Evolution of American Street Network Planning and Design.} Target: \textit{Journal of the American Planning Association}, Winter 2019.

        \item[\the\year] \tab Boeing, G., M. Batty, S. Jiang, D. Mahmoudi. \enquote{Urban Analytics.} Target: \textit{Handbook of Spatial Analysis in the Social Sciences}, edited by S. Rey and R. Franklin. Cheltenham, UK: Edward Elgar Publishing. Spring 2020.
        
        \item[\the\year] \tab Boeing, G. \enquote{Street Network Analysis in Urban Science and Planning.} Target: \textit{Transactions in GIS}, Spring 2020.

    \end{tablist}



    \section*{Invited Talks}

    \begin{tablist}

        \item[2019] \tab \enquote{Urban Data Science: Street Networks and Travel Behavior.} Evidation Health, Data Science Seminar Series. Santa Barbara, California. May 16.
        
        \item[2019] \tab \enquote{Network Science for Urban Transportation Modeling and Long-Range Planning.} MIT Megacity Logistics Lab at the Center for Transportation and Logistics. Cambridge, Massachusetts. May 9.

        \item[2019] \tab \enquote{Computational Modeling and Analysis in Transportation System Design.} Cornell University, Systems Engineering Seminar Series. Ithaca, New York. Apr 12.

        \item[2019] \tab \enquote{Growth, Access, and Resilience as Urban Technology Paradigms Shift.} The World Bank, Global Facility for Disaster Reduction and Recovery. Washington, DC. Apr 3.

        \item[2018] \tab \enquote{Computational Urban Street Network Analysis.} Virginia Tech, Urban Computing Seminar Series. Arlington, Virginia. Dec 4.

        \item[2018] \tab \enquote{Urban Science and Street Networks.} Massachusetts Institute of Technology, Department of Urban Studies and Planning. Cambridge, Massachusetts. Nov 27.
        
        \item[2018] \tab \enquote{Introduction to Street Network Analysis with OSMnx.} University of Helsinki, Digital Geography Lab (remote/recorded interview). Helsinki, Finland. Nov 16.

        \item[2018] \tab \enquote{Urban Street Network Science with OSMnx.} Tufts University, Department of Urban and Environmental Policy and Planning. Somerville, Massachusetts. Nov 15.

        \item[2018] \tab \enquote{Free Data for Free Spaces: Democratizing and Disseminating Spatial Network Data and Models for Better Urban Planning.} Venice Biennale of Architecture. Venice, Italy. Oct 24.

        \item[2018] \tab \enquote{Online Rental Housing Market Representation and the Digital Reproduction of Urban Inequality.} Harvard University, Joint Center for Housing Studies. Cambridge, Massachusetts. Sep 20.

        \item[2018] \tab \enquote{Urban Street Network Science: Modeling, Simulating, and Visualizing Complex Transportation Systems.} Uber Technologies. San Francisco, California. Aug 20.

        \item[2018] \tab \enquote{The Study of Street Networks in Urban Data Science.} NYU Center for Data Science. New York, New York. Apr 18.

        \item[2018] \tab \enquote{Computational Street Network Analysis in Urban Form Studies.} Columbia University Graduate School of Architecture, Planning, and Preservation. New York, New York. Apr 17.

        \item[2018] \tab \enquote{Scalable Methods for Acquiring, Analyzing, and Visualizing Urban Street Networks.} NYU Center for Urban Science and Progress, Applied Urban Science Group. Brooklyn, New York. Apr 16.

        \item[2018] \tab \enquote{Studying Urban Form and Resilience through Large-Scale Street Network Analysis.} University of California, Santa Barbara, Department of Geography. Santa Barbara, California. Jan 30.

        \item[2018] \tab \enquote{Seeing Cities through New Technologies and Big Data.} University of Oregon, School of Planning, Public Policy, and Management. Eugene, Oregon. Jan 25.

        %\item[2018] \tab \enquote{Urban Form, Sustainability, and Large-Scale Street Network Analysis.} Northeastern University, School of Public Policy and Urban Affairs. Boston, Massachusetts. Jan 18.

        \item[2018] \tab \enquote{Understanding Urban Form and Circulation through Large-Scale Street Network Analysis.} Dartmouth College, Department of Geography. Hanover, New Hampshire. Jan 15.

        \item[2017] \tab \enquote{Street Network Analyses of Urban Form Resilience and Equity.} University of Chicago, Mansueto Institute for Urban Innovation. Chicago, Illinois. Nov 2.

        \item[2017] \tab \enquote{Measuring Urban Form Sustainability with Topological and Geometric Street Network Analysis.} Stanford University, Sustainable Urban Systems Initiative. Palo Alto, California. Oct 26.

        \item[2017] \tab \enquote{Graph-Theoretic Representation and Analysis of Urban Street Networks.} Montana State University, Department of Computer Science. Bozeman, Montana. Oct 16.

        \item[2017] \tab \enquote{OpenStreetMap Network Data for Transportation Planning.} Remix Transit Planning. San Francisco, California. Aug 16.

        \item[2017] \tab \enquote{Street Networks: Urban Form and Resilience.} University of Florida, Department of Urban and Regional Planning. Gainesville, Florida. May 8.

        \item[2017] \tab \enquote{Scalable Methods for Acquiring, Analyzing, and Visualizing Urban Street Networks.} The Santa Fe Institute. Santa Fe, New Mexico. Feb 2.

        \item[2016] \tab \enquote{Urban Data Science for Studying Housing Affordability and Urban Form.} NYU Center for Urban Science and Progress. Brooklyn, New York. Dec 14.

        \item[2016] \tab \enquote{New Insights into Rental Housing Markets: Web Scraping and Analyzing Craigslist Rental Listings.} City of Oakland. Oakland, California. May 12.

        \item[2016] \tab \enquote{New Insights into Rental Housing Markets: Web Scraping and Analyzing Craigslist Rental Listings.} City of San Francisco, Citywide Planning Division. San Francisco, California. Apr 19.

        \item[2016] \tab \enquote{Smart Cities, Technology, and Representation: Prospects and Challenges.} Adobe Systems Sustainability Speaker Series. San Jose, California. Jan 28.

    \end{tablist}

    \subsection*{Campus Talks}

    \begin{tablist}

        \item[2018] \tab \enquote{Urban Street Network Science with OSMnx.} Northeastern University Seattle Campus. Seattle, Washington. Nov 28.

        \item[2018] \tab \enquote{The Legibility of Urban Spatial Order in Computational Street Network Analysis.} NUVis: Northeastern University Visualization Consortium. Boston, Massachusetts. Oct 18.

        \item[2017] \tab \enquote{Urban Street Network Analysis with OSMnx.} Geospatial Innovation Facility, College of Natural Resources, University of California, Berkeley. Berkeley, California. Oct 5.

    \end{tablist}


    \section*{Conference Activity}

    \subsection*{Plenary/Keynote Addresses}

    \begin{tablist}

        \item[2019] \tab \enquote{Geographic Information, Spatial Networks, and the New Urban Science.} American Association of Geographers Annual Meeting, 8\textsuperscript{th} annual \emph{Transactions in GIS} plenary address. Washington, DC. Apr 3--7.

        \item[2018] \tab \enquote{The Legible and the Illegible: Urban Science, City Design, and Human Circulation.} The Architect of the Future Conference. Moscow, Russia. Sep 10--11.

    \end{tablist}

    \subsection*{Sessions Organized}

    \begin{tablist}

        \item[2017] \tab \enquote{Emerging Computational Methods in Urban Design.} Association of Collegiate Schools of Planning Annual Conference. Denver, Colorado. Oct 12--15.

    \end{tablist}

    \subsection*{Sessions Chaired/Moderated}

    \begin{tablist}

        \item[2019] \tab \enquote{Machine Learning Methods.} Association of Collegiate Schools of Planning Annual Conference. Greenville, South Carolina. Oct 24--27.
        
        \item[2019] \tab \enquote{Social Systems.} International Conference on Network Science. Burlington, Vermont. May 27--31.
        
        \item[2018] \tab \enquote{Smart Cities Technologies for Transportation Systems.} Smart Cities: Critical Infrastructure Symposium. Seattle, Washington. Nov 29.

    \end{tablist}

    \subsection*{Invited Panelist}

    \begin{tablist}

        \item[2019] \tab \enquote{Urban Data Science: Methods and Models for Our Changing Cities.} Panelist with Vanessa Frias-Martinez, Wenfei Xu, Song Gao, and Ate Poorthuis; chaired by Levi Wolf and Wei Kang. American Association of Geographers Annual Meeting. Washington, DC. Apr 3--7.
        
        \item[2018] \tab \enquote{Big Ideas Session on Civic Analytics and Urban Science.} Panelist with Luis Bettencourt, Marta González, and Sarah Williams; chaired by Constantine Kontokosta. Association of Collegiate Schools of Planning Annual Conference. Buffalo, New York. Oct 25--28.

        \item[2018] \tab \enquote{Who Benefits from \enquote{Smart City} Technologies? How Can They Be a Piece of the Puzzle Toward Social and Environmental Justice?} Panelist with Lisa Schweitzer, Clint Andrews, and Tom Sanchez; chaired by Mehdi Heris. Association of Collegiate Schools of Planning Annual Conference. Buffalo, New York. Oct 25--28.

        \item[2017] \tab \enquote{Public Communication Strategies for Planning Academics.} Panelist with Jennifer Dill, Yingling Fan, and Justin Hollander; chaired by Carissa Slotterback. Association of Collegiate Schools of Planning Annual Conference. Denver, Colorado. Oct 12--15.

    \end{tablist}

    \subsection*{Conference Presentations}

    Presenting author \textit{italicized}, if other.\bigskip
    % Asterisk* indicates paper published in \enquote{Peer-Reviewed Proceedings} above.

    \begin{tablist}
    	
    	\item[2020] \tab Boeing, G. \enquote{The Street Grid and Car Ownership: Trends in US Transportation Network Design.} Transportation Research Board 99\textsuperscript{th} Annual Meeting. Washington, DC. Jan 12--16.
    	
    	\item[2019] \tab Boeing, G. \enquote{Symposium: Setting the Spatial Data Science Agenda.} Spatial Data Science Symposium. Santa Barbara, California. Dec 9--11.

        \item[2019] \tab Boeing, G. \enquote{Off the Grid: The Evolution of American Street Network Planning and Design.} Association of Collegiate Schools of Planning Annual Conference. Greenville, South Carolina. Oct 24--27.

        \item[2019] \tab Boeing, G. and \textit{W. Riggs} \enquote{Converting One-Way Streets to Two-Way Streets to Improve Transportation Network Efficiency and Reduce Emissions.} Association of Collegiate Schools of Planning Annual Conference. Greenville, South Carolina. Oct 24--27.

        \item[2019] \tab Boeing, G. \enquote{Urban Spatial Order: Street Network Orientation, Configuration, and Entropy.} International Conference on Network Science. Burlington, Vermont. May 27--31.

        \item[2019] \tab Boeing, G. \enquote{The Legibility of Urban Form: Spatial Information Platforms and Visualization.} International Conference on Urban Experience and Design. Medford, Massachusetts. Apr 26.

        \item[2019] \tab Boeing, G. \enquote{Online Rental Housing Market Representation and the Digital Reproduction of Urban Inequality.} Boston Area Research Initiative Annual Conference. Boston, Massachusetts. Apr 26.

        \item[2019] \tab Boeing, G. \enquote{The Evolution of American Street Network Design and Planning.} Urban Affairs Association Annual Conference. Los Angeles, California. Apr 24--27.

        \item[2019] \tab Abdelkader, A., G. Boeing, \textit{B.~T. Fasy}, and D.~L. Millman. \enquote{Local Persistent Homology-Based Distances between Nonplanar Road Networks.} Joint Mathematics Meetings. Baltimore, Maryland. Jan 16--19.

        \item[2018] \tab \textit{Abdelkader, A.}, G. Boeing, B.~T. Fasy, and D.~L. Millman. \enquote{Topological Distance Between Nonplanar Transportation Networks.} Fall Workshop on Computational Geometry. Queens, New York. Oct 26--27.

        \item[2018] \tab Boeing, G. \enquote{Sociodemographic Representation of Online Rental Housing Listings: Information Surpluses and Deficits.} Association of Collegiate Schools of Planning Annual Conference. Buffalo, New York. Oct 25--28.

        \item[2018] \tab \textit{Waddell, P.}, I. Garcia-Dorado, S. Maurer, G. Boeing, M. Gardner, E. Porter, and D. Aliaga. \enquote{Urban Modeling Without Zones: A Metropolitan Graph-Based Microsimulation of Real Estate Markets and Transportation.} Association of Collegiate Schools of Planning Annual Conference. Buffalo, New York. Oct 25--28.

        \item[2018] \tab Boeing, G. \enquote{Transportation Network Modeling and Urban Equity.} Dukakis Center for Urban and Regional Policy Transportation Equity Conference. Boston, Massachusetts. Oct 19.

        \item[2018] \tab \textit{Waddell, P.}, I. Garcia-Dorado, S. Maurer, G. Boeing, M. Gardner, E. Porter, and D. Aliaga. \enquote{Architecture for Modular Microsimulation of Real Estate Markets and Transportation.} Symposium on Applied Urban Modelling. Cambridge, England. Jun 27--29.

        \item[2017] \tab Boeing, G. \enquote{New Methods for Acquiring and Analyzing Worldwide Street Network Data: A Multiscale Analysis of 27,000 Urban Street Networks.} Association of Collegiate Schools of Planning Annual Conference. Denver, Colorado. Oct 12--15.

        \item[2016] \tab Boeing, G. \enquote{Craigslist and U.S. Rental Housing Markets.} American Planning Association Annual Conference. Phoenix, Arizona. Apr 2--5.

        \item[2016] \tab Boeing, G. \enquote{Understanding Informal Rental Housing Markets through Public Data.} American Association of Geographers. San Francisco, California. Mar 29--Apr 2.

        \item[2016] \tab Barajas, J.~M., G. Boeing, and \textit{J. Wartell}. \enquote{Neighborhood Change, One Pint at a Time: The Impact of Local Characteristics on Craft Breweries.} Urban Affairs Association Annual Conference. San Diego, California. Mar 16--19.

        \item[2015] \tab Boeing, G. \enquote{Methods for Measuring the Aggregate Complexity Outcomes of Urban Design.} International Conference on Complex Systems. Tempe, Arizona. Sep 28--Oct 2.

        \item[2015] \tab Boeing, G. \enquote{Pedagogy of Urban Informatics.} Environmental Design Circus. Berkeley, California. Mar 6.

        \item[2014] \tab Boeing, G. and P. Waddell. \enquote{Web Scraping Urban Data: Lessons from the Lab and the Classroom.} Association of Collegiate Schools of Planning Annual Conference. Philadelphia, Pennsylvania. Oct 30--Nov 2.

        \item[2014] \tab Boeing, G., D. Church, H. Hubbard, J. Mickens, and L. Rudis. \enquote{LEED-ND and Perceptions of Livability.} Environmental Design Circus. Berkeley, California. Mar 13.

    \end{tablist}



    \section*{Grants and Awards}

    \subsection*{Awards and Honors}

    \begin{tablist}

        \item[2019] \tab Network Science Society Visualization Prize finalist

        \item[2018] \tab Information Is Beautiful Awards shortlist

        \item[2014] \tab Kaye Bock Award, best journal article

        \item[2010] \tab Accenture Inventor Innovation Award

    \end{tablist}

    \subsection*{Grants and Fellowships}

    \begin{tablist}

        \item[2020] \tab Civic Infrastructure, Domain-Specific Chatbots, and Public Information Dissemination (\$200,000). The Public Good Projects research grant. PI.
        
        \item[2019] \tab Urban Form Impact: Humans, Environment, Equity (\$50,000). Northeastern University Tier 1 research grant. Co-PI with Sara Carr and Jana Cephas.

        \item[2019] \tab NU CSSH summer research matching grant (\$6,000). PI.

        \item[2019] \tab NU Lab for Maps, Texts, and Networks research grant (\$2,500). PI.

        \item[2018] \tab ACSP FWIG Emerging Scholar travel grant (\$500)

        \item[2018] \tab NU Lab for Maps, Texts, and Networks travel grant (\$1,000)

        \item[2018] \tab Northeastern University research fund (\$25,000)

        \item[2017] \tab University of California Doctoral Completion Fellowship (\$36,655)

        \item[2016] \tab UC Berkeley DCRP travel grant (\$500)

        \item[2016] \tab University of California Graduate Division travel grant (\$900)

        \item[2015] \tab UC Berkeley DCRP travel grant (\$500)

        \item[2012] \tab University of California Regents' Fellowship (\$158,025/4 years)

    \end{tablist}



    \section*{Teaching Experience}

    \subsection*{University of Southern California}
    
    \begin{itemize}
    	
    	\item Urban Informatics
    	\item Data, Evidence, and Communication for the Public Good
    
	\end{itemize}
    	
    \subsection*{Northeastern University}

    \begin{itemize}

        \item Urban Theory and Science
        \item Advanced Spatial Analysis of Urban Systems
        \item Big Data for Cities

    \end{itemize}

    \subsection*{University of California, Berkeley}

    \begin{itemize}

        \item Urban Informatics and Visualization

    \end{itemize}

    \subsection*{Planetizen}

    \begin{itemize}

        \item Python for Planners
        \item Data Analysis and Visualization for Planners
        \item Geospatial Data Analysis
        \item Street Network Analysis

    \end{itemize}


    \section*{Service}

    \subsection*{Journal Peer Review}

    \begin{itemize}
        
        \item \textit{American Journal of Sociology}
        
        \item \textit{Case Studies on Transport Policy}

        \item \textit{Cities}

        \item \textit{Computers, Environment and Urban Systems}

        \item \textit{Environment and Planning B: Urban Analytics and City Science}

        \item \textit{European Physical Journal: Data Science}

        \item \textit{International Journal of Geographical Information Science}

        \item \textit{International Planning Studies}

        \item \textit{International Regional Science Review}

        \item \textit{ISPRS International Journal of Geo-Information}

        \item \textit{Journal of the American Planning Association}

        \item \textit{Journal of Open Source Education}
        
        \item \textit{Journal of Planning Education and Research}

        \item \textit{Journal of Transport Geography}

        \item \textit{Journal of Transport and Land Use}
        
        \item \textit{Journal of Urban Technology}

        \item \textit{Landscape and Urban Planning}

        \item \textit{Mathematics}

        \item \textit{Nonlinear Dynamics}

        \item \textit{PLOS One}
        
        \item \textit{Scientific Reports}
        
        \item \textit{Social Forces}
        
        \item \textit{Social Indicators Research}

        \item \textit{Sustainable Cities and Society}

        \item \textit{Transactions in GIS}

        \item \textit{Transport Findings}
        
        \item \textit{Transport Reviews}
        
        \item \textit{Transportation Research Record}

        \item \textit{Urban Design International}

        \item \textit{Urban Science}

    \end{itemize}

	\subsection*{Academic Press Peer Review}
	
	\begin{itemize}
		
		\item Cambridge University Press
		
	\end{itemize}

    \subsection*{Funding Agency Peer Review}

    \begin{itemize}

        \item National Science Foundation

        \item Social Sciences and Humanities Research Council of Canada

    \end{itemize}

    \subsection*{Service to Field}

    \begin{itemize}

        \item Task Force on Outreach and Engagement, Association of Collegiate Schools of Planning, 2019--
        
        \item Program Committee, Future Cities Challenge, 2019--

        \item Review and Appraisal Committee, Association of Collegiate Schools of Planning, 2018--

        \item Scientific Committee, Symposium on Simulation for Architecture and Urban Design, 2018--

        \item Book review editor, \textit{Berkeley Planning Journal}, 2013--14

    \end{itemize}

    \subsection*{Service to Department}

    \begin{itemize}

        \item Standing Committee on Digital Proficiencies and Quantitative Methods, NU CSSH, 2018--19

        \item Ph.D. program faculty representative, UC Berkeley DCRP, 2015--16

        \item Ph.D. program admissions committee, UC Berkeley DCRP, 2015--16

    \end{itemize}

    \subsection*{Studio Review Jury}
    
    \begin{itemize}
        
        \item MIT, Workshop on Geographic Information Systems (Prof. Sarah Williams), Fall 2018
    
    \end{itemize}


    \section*{Professional Affiliations}

    \begin{itemize}

        \item American Association of Geographers

        \item American Planning Association

        \item Association of Collegiate Schools of Planning

        \item Association for Computing Machinery

        \item Complex Systems Society
        
        \item Network Science Society

        \item New York Academy of Sciences

        \item Project Management Institute

        \item Python Software Foundation
        
        \item Regional Studies Association

        \item Urban Affairs Association

    \end{itemize}



    \section*{Credentials}

    \begin{itemize}

        \item U.S. Department of Defense secret clearance

        \item U.S. Department of Homeland Security public trust

        \item Project Management Professional (PMP)

    \end{itemize}



    \section*{Consulting Engagements}

    \begin{tablist}

        \item[2017--19] \tab The Public Good Projects

        \item[2017--18] \tab Calthorpe Analytics

        \item[2016--18] \tab UrbanSim Inc.

        \item[2013--18] \tab Avalon Health Economics

        \item[2013]     \tab Raimi \& Associates

        \item[2009--13] \tab Accenture

    \end{tablist}



    \section*{Professional Experience}

    \begin{tablist}

        \item[2009--13] \tab Accenture, Consultant and Project Manager\\
                             London, England; New York, New York; San Diego, California

        \item[2007--09] \tab Permission Data, Front-End Systems Product Manager\\
                             New York, New York

        \item[2004--07] \tab Acumen Inc., Web Systems Developer\\
                             Mesa, Arizona

    \end{tablist}



    \section*{Selected Media Coverage}

    Complete listing and links available at \href{https://geoffboeing.com/press/}{https://geoffboeing.com/press/} \bigskip

    \begin{tablist}

        \item[2019] \tab \textit{PBS NOVA}. \enquote{With \enquote{Problems Out There Waiting for Us,} Public Health Practitioners Turn to AI for Help.} Apr 11.
        
        \item[2018] \tab \textit{CityLab}. \enquote{Visualizing the Hidden Logic of Cities.} Jul 26.

        \item[2018] \tab \textit{99 Percent Invisible}. \enquote{On the Grid: Visualizing Street Network Orientations Across 50 Global Cities.} Jul 20.

        \item[2018] \tab \textit{Slate}. \enquote{Elegant Graphs Reduce 25 American Cities to Their Design Essence.} Jul 11.

        \item[2017] \tab \textit{The San Francisco Chronicle}. \enquote{Stunning, Simple Maps Show San Francisco versus Other Global Cities.} Jun 19.

        \item[2017] \tab \textit{Forbes}. \enquote{Understanding Our Cities, Thanks to Beautiful Maps.} Feb 7.

        \item[2017] \tab \textit{Fast Company}. \enquote{Turn Your Local Streets into a Map That Reveals the Character of Your Neighborhood.} Feb 6.

        \item[2017] \tab \textit{CityLab}. \enquote{A Digital Window into Your City's Urban Form.} Jan 17.

        \item[2016] \tab \textit{The Washington Post}. \enquote{What More Than 1 Million Craigslist Rental Listings Tell Us about the Housing Market.} Sep 1.

        \item[2016] \tab \textit{Fast Company}. \enquote{11 Million Craigslist Ads Show Which Cities Have the Highest Rents.} Sep 1.

        \item[2016] \tab \textit{NextCity}. \enquote{What 11 Million Craigslist Posts Show About Affordable Housing.} Aug 26.

    \end{tablist}



    \section*{Technical Skills}

    \subsection*{Statistical and Computational Methods}

    \begin{itemize}

        \item Computational statistics and machine learning, systems analysis, data mining, data wrangling, Python (including numpy, scipy, pandas, matplotlib, statsmodels, networkx, and scikit-learn), JavaScript, HTML, web scraping, MySQL, Postgres, and various other databases.

    \end{itemize}

    \subsection*{Geospatial Methods}

    \begin{itemize}

        \item Spatial analysis, network analysis, PostGIS, QGIS, geopandas, PySAL, Leaflet, CARTO, agent-based spatial modeling and microsimulation. I developed and maintain the OSMnx street network modeling software.

    \end{itemize}



    % display today's date as Month Year after a vertical space below the end of the text
    %\begin{center}
        %\vspace{6em}
        %\vfill
        %Updated \monthyeardate\today
    %\end{center}


\end{document}
