% Geoff Boeing - Curriculum Vitae
%
% Copyright (C) 2017 Geoff Boeing
% Email: gboeing@berkeley.edu
% Web: http://geoffboeing.com/

\documentclass[11pt,letterpaper]{report}

% load packages
\usepackage{hyperref} % enable hyperlinks
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{fontspec} % define custom fonts
\usepackage{sectsty} % allow custom section fonts
\usepackage[USenglish]{babel} % use american-style formatting
\usepackage[autostyle]{csquotes} % enable enquoting
\usepackage{datetime} % enable formatting of date output

% define a default font face and set it as the body font
\newcommand{\defaultfontface}{Minion Pro}
\setmainfont{\defaultfontface}

% set title font
\newfontfamily\titleface{\defaultfontface}
\newcommand{\titlefont}[1]{{\titleface\bfseries\Huge{#1}}}

% set section and subsection heading fonts
\newfontfamily\sectionface{\defaultfontface}
\newfontfamily\subsectionface{\defaultfontface}
\sectionfont{\sectionface\mdseries\large\bfseries\uppercase}
\subsectionfont{\subsectionface\mdseries\normalsize\bfseries}

% set page margins
\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% prevent paragraph indentation
\setlength\parindent{0em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
      \setlength{\leftmargin}{1.75em}
      \setlength{\itemsep}{0.25em}
      \setlength{\parskip}{0em}
      \setlength{\parsep}{0.25em}
    }
}{
  \end{list}
}

% customize compact spacing of ordered lists
\setlist[enumerate]{itemsep=0.25em, leftmargin=1.75em}

% print the month and year only when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define metadata for pdf properties
\newcommand{\myname}{Geoff Boeing}
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\myname},
  pdfkeywords = {urban planning, urban design, data science, complexity},
  pdftitle = {\myname: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}



\begin{document}

% display my name as the document title
\titlefont{\myname}

% contact info
\vspace{1em}
\begin{minipage}[t]{0.495\textwidth}
  Department of City and Regional Planning \\
  University of California, Berkeley \\
  Berkeley, California 94720
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  Email: \href{mailto:gboeing@berkeley.edu}{gboeing@berkeley.edu} \\
  Web: \href{http://geoffboeing.com/}{http://geoffboeing.com/} \\
  Phone: +1-917-267-2297
\end{minipage}
\vspace{1em}



\section*{Education}

\subsection*{University of California, Berkeley}
\begin{itemize}
\item Ph.D. City and Regional Planning, 2017 (expected).   
  \begin{itemize}
  \item Dissertation: \enquote{Methods and Measures for Analyzing Complex Street Networks and Urban Form.}
  \item Committee: Paul Waddell (chair), Robert Cervero, Elizabeth Macdonald, David O'Sullivan.
  \end{itemize}  
\end{itemize}
  
\subsection*{Arizona State University}
\begin{itemize}
\item M.S. Information Management, 2006.
\item B.S. Computer Information Systems, 2004.  
  \begin{itemize}
  \item Graduated \emph{summa cum laude} from the Barrett Honors College.
  \item Minor, Psychology.
  \end{itemize}
\end{itemize}



\section*{Research and Teaching Interests}

\begin{itemize}
\item Urban planning and transportation-land use policy.
\item Urban form, including history and theories of form/design and contemporary paradigms.
\item Rental housing markets and affordability.
\item Urban data science: computational statistics, data visualization, spatial analysis, Python, big data.
\item Complex systems: complexity theories of cities, systems thinking, network analysis.
\end{itemize}



\section*{Publications}

\subsection*{Peer-Reviewed Journal Articles}

\begin{enumerate}

\item Boeing, G. and P. Waddell. 2016. \enquote{New Insights into Rental Housing Markets across the United States: Web Scraping and Analyzing Craigslist Rental Listings.} \emph{Journal of Planning Education and Research}, published online before print.

\item Boeing, G. 2016. \enquote{Honolulu Rail Transit: International Lessons from Barcelona in Linking Urban Form, Design, and Transportation.} \emph{Planext} 2, 28--47.

\item Boeing, G. 2016. \enquote{Visual Analysis of Nonlinear Dynamical Systems: Chaos, Fractals, Self-Similarity, and the Limits of Prediction.} \emph{Systems} 4(4), 37.

\item Boeing, G., D. Church, H. Hubbard, J. Mickens, and L. Rudis. 2014. \enquote{LEED-ND and Livability Revisited.} \emph{Berkeley Planning Journal} 27(1), 31--55.

\end{enumerate}



\subsection*{Journal Article Manuscripts Under Review}

\begin{enumerate}[resume]

\item Boeing, G. 2017. \enquote{The Effects of Inequality, Density, and Heterogeneous Residential Preferences on Urban Displacement and Metropolitan Structure: An Agent-Based Model.} Revise and resubmit at \emph{Journal of Artificial Societies and Social Simulation}.

\item Boeing, G. 2017. \enquote{OSMnx: New Methods for Acquiring, Constructing, Analyzing, and Visualizing Complex Street Networks.} Revise and resubmit at \emph{Computers, Environment and Urban Systems}.

\end{enumerate}



\subsection*{Book Chapters and Other Articles}

\begin{enumerate}[resume]

\item Barajas, J.~M., G. Boeing, and J. Wartell. 2017. \enquote{Neighborhood Change, One Pint at a Time: The Impact of Local Characteristics on Craft Breweries.} In: \emph{Untapped: Exploring the Cultural Dimensions of Craft Beer}, edited by N.~G. Chapman, J.~S. Lellock, and C.~D. Lippard. Morgantown, WV: West Virginia University Press.

\item Boeing, G. 2017. \enquote{Understanding Cities through Networks and Flows.} \emph{Berkeley Planning Journal} 28(1), 118--123.

\item Boeing, G. 2016. \enquote{How Our Neighborhoods Lost Food, and How They Can Get It Back.} \emph{Progressive Planning} 206(Winter), 35--37.

\end{enumerate}



\subsection*{Patents}

\begin{enumerate}[resume]

\item Beck, A.~E., G. Boeing, and D. Shannon. 2014. \emph{Systems and Methods for Analyzing Requirements}. Patented in various jurisdictions as: United States patent US8650186B2, European patent EP2413256, Australian patent AU2011204935, Canadian patent CA2747481, and Chinese patent CN102346763.

\end{enumerate}



\subsection*{Manuscripts in Preparation}

\begin{enumerate}[resume]

\item Boeing, G. 2017. \enquote{Socio-demographic and Spatial Representation of Online Rental Listings: Evidence from Craigslist.}

\item Boeing, G. 2017. \enquote{New Methods for Collecting and Analyzing Historical Online Rental Listings.}

\item Boeing, G. 2017. \enquote{Comparative Visualization of Urban Form and Street Networks: Planning and Communication Tools for Urban Designers.}

\item Boeing, G. 2017. \enquote{A Multi-Scale Analysis of 27,000 Urban Street Networks.}

\item Boeing, G. 2017. \enquote{Methods for Measuring the Complexity of Urban Form and Design.}

\item Nguyen, D. and G. Boeing. 2017. \enquote{Economic Trends in Craigslist's Online Market for Used Cars.}

\end{enumerate}



\section*{Conference Presentations}

\begin{itemize}

\item 2016. \enquote{Craigslist and U.S. Rental Housing Markets.} American Planning Association Annual Conference. Phoenix, Arizona.

\item 2016. \enquote{Understanding Informal Rental Housing Markets through Public Data.} Association of American Geographers Annual Meeting. San Francisco, California.

\item 2015. \enquote{Methods for Measuring the Aggregate Complexity Outcomes of Urban Design.} International Conference on Complex Systems. Tempe, Arizona.

\item 2015. \enquote{Pedagogy of Urban Informatics.} College of Environmental Design Circus. Berkeley, California.

\item 2014. \enquote{Web Scraping Urban Data: Lessons from the Lab and the Classroom.} American Collegiate Schools of Planning Annual Conference. Philadelphia, Pennsylvania.

\item 2014. \enquote{LEED-ND and Perceptions of Livability.} College of Environmental Design Circus. Berkeley, California.

\end{itemize}



\section*{Invited Talks}

\begin{itemize}

\item 2017. \enquote{Scalable Methods for Acquiring, Analyzing, and Visualizing Urban Street Networks.} The Santa Fe Institute. Santa Fe, New Mexico.

\item 2016. \enquote{Urban Data Science for Studying Housing Affordability and Urban Form.} NYU Center for Urban Science and Progress. Brooklyn, New York.

\item 2016. \enquote{Smart Cities, Technology, and Representation: Prospects and Challenges.} Adobe Systems. San Jose, California.

\end{itemize}



\section*{Teaching Experience}

\subsection*{University of California, Berkeley}

\begin{itemize}
\item Urban Informatics and Visualization, co-lead instructor (Fall 2013, Fall 2014, Fall 2015, Fall 2016).
  \begin{itemize}	
  \item Graduate-level data science course that teaches urban data analysis, computational statistics, visualization, and mapping using the Python programming language, open source analysis/visualization tools, and public data. Provides future city planners with a modern toolkit of technical skills for computational problem solving, reproducible research, policy analysis, and advocacy.
  \end{itemize}
\end{itemize}



\section*{Service Positions}

\subsection*{University of California, Berkeley}

\begin{itemize}
\item Ph.D. program faculty representative, 2015--2016.
\item Book review editor, \emph{Berkeley Planning Journal}, 2013--2014.
\end{itemize}


\section*{Fellowships, Grants, and Awards}

\begin{itemize}
\item University of California Doctoral Completion Fellowship, 2016--2017.
\item University of California Graduate Division Travel Grant, 2016.
\item University of California Regents' Fellowship, 2012--2016.
\item Kaye Bock Award for Best Journal Article, 2014.
\item Accenture Inventor Innovation Award, 2010.
\item Honeywell Scholarship Award, 2003--2004.
\item Exxon Computer Information Systems Award, 2002--2003.
\item Samuel and Lorraine Reich Endowed Scholarship, 2002--2003.
\item Jerry Wistosky Memorial Scholarship, 2002--2003.
\item Alumni Association L. William Seidman Scholarship, 2002--2003.
\item AAL Scholarship Award, 2000--2004.
\end{itemize}



\section*{Professional Affiliations}

\begin{itemize}
\item Member, American Planning Association.
\item Member, Association of American Geographers.
\item Member, Complex Systems Society.
\item Member, Association for Computing Machinery.
\item Member, Project Management Institute.
\end{itemize}



\section*{Consulting Engagements}

\begin{itemize}
\item Calthorpe Associates, 2017--present.
\item UrbanSim Inc., 2016--present.
\item Raimi \& Associates, 2013.
\item Avalon Health Economics, 2013--present.
\item Accenture, 2009--2013.
\end{itemize}



\section*{Professional Experience}

\subsection*{Unversity of California, Berkeley}

\begin{itemize}
\item Graduate Student Researcher and Instructor, 2013--2016.
\item Led affordable housing research project in the Urban Analytics Lab, collecting and analyzing big data from Craigslist rental listings. Co-taught Urban Informatics and Visualization course. Lecturer at the UC Berkeley D-Lab.
\end{itemize}

\subsection*{Accenture}
  
\begin{itemize}
\item Project Manager and Consultant, 2009--2013.
\item Led an international development knowledge management project to re-engineer how livelihoods information and knowledge resources are shared across cultural and geographical boundaries. Researched and developed information discovery tools and databases, using semantic ontologies and natural language processing.
\end{itemize}

\subsection*{Permission Data}
  
\begin{itemize}
\item Front-End Systems Product Manager, 2007--2009.
\item Developed data brokering systems for large data sets. Led collaborative teams to gather requirements, design, and build front-end systems and web services.
\end{itemize}

\subsection*{Acumen, Inc.}
  
\begin{itemize}
\item Web Systems Developer, 2004--2007.
\item Enterprise information systems analysis, design, development, and support for a non-profit organization. Designed and built online enterprise systems, reporting systems, and back-end databases.
\end{itemize}



\section*{Skills and Methods}

\subsection*{Statistical and Computational Methods}

\begin{itemize}
\item Multivariate statistics and various machine learning algorithms, systems analysis, data mining, data wrangling and ETL, Python (including numpy, scipy, pandas, matplotlib, statsmodels, networkx, and scikit-learn), web scraping, agent-based modeling and microsimulation (including UrbanSim, NetLogo, and Mesa), R, Java, .NET, PHP, HTML, MySQL, Postgres, and various other databases.
\end{itemize}

\subsection*{Geospatial Methods}

\begin{itemize}
\item GIS, spatial analysis, network analysis, QGIS, ArcGIS, PostGIS, geopandas, urban modeling and simulation, Leaflet, Mapbox.
\end{itemize}

\subsection*{Project Management}

\begin{itemize}
\item I am a credentialed Project Management Professional (PMP), and have managed projects and led various teams in academia, the public sector, and the private sector.
\end{itemize}

\subsection*{International Experience}

\begin{itemize}
\item I have previously worked professionally in the United States, the United Kingdom, Malawi, Mozambique, South Africa, Cambodia, and Thailand.
\end{itemize}

\subsection*{Security Clearance}

\begin{itemize}
\item U.S. Department of Defense: secret clearance.\\U.S. Department of Homeland Security: public trust.
\end{itemize}


% display today's date as MONTH YEAR after a vertical space below the end of the text
\begin{center}
\vspace{6em}
%\vfill
Updated \monthyeardate\today
\end{center} 



\end{document}